### 2019-03-16 README.Rmd
Tweak README

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ecohealthalliance/citesdb?branch=master&svg=true){data-external="1"}](https://ci.appveyor.com/project/ecohealthalliance/citesdb)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![CRAN status](https://www.r-pkg.org/badges/version/citesdb){data-external="1"}](https://cran.r-project.org/package=citesdb)

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>.

More details on the database can be found in the `?guidance` help file.

>>>>

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife
products subject to oversight under the Convention on International Trade in Endangered Species).
